---
title: "apm_chemmanproc_modeling"
author: "Kevin Cooper"
date: "1/12/2021"
output: github_document
---

The purpose of this is to take a look at Max Kuhn's Applied Predictive Modeling, particularly at the Chemical Manufacturing Process dataset. Also a goal of mine has been to learn tidymodeling a little more.

# Data Ingestion 
```{r, results='hide', message = FALSE,}
require(AppliedPredictiveModeling)

#This process is ugly, can fix later.
data(ChemicalManufacturingProcess)
df <- ChemicalManufacturingProcess
rm(ChemicalManufacturingProcess)
```
## Get Libraries 
```{r, warning = FALSE, message = FALSE, results = 'hide'}
require(here)
source(here("project_config.R"))
```

# Data Overview & Quality 
Incredibly small dataset. It's either one extreme or another.
```{r}
dim(df)
```
All variables are numeric. This never happens in the real world.
```{r}
sapply(df,class)
```

The names look incredibly unuseful from a process standpoint.
```{r}
names(df)
```
Let's take a look at empties. Steal more code from here:
https://jenslaufer.com/data/analysis/visualize_missing_values_with_ggplot.html

This isn't the prettiest, and not normally what I go after, but achieves the purpose.
```{r, fig.width = 8, fig.height = 6}
na_vals <- function(df){
  p <- df %>% 
    mutate(id = row_number()) %>% 
    gather(-id, key = "key", value = "val") %>% #Should update this to pivot_longer later
    mutate(isna = is.na(val)) %>% 
    ggplot(aes(x = key, y = id, fill = isna)) +
    geom_raster(alpha = 0.8) +
    scale_fill_manual(name = "",
                      values = c("steelblue","tomato3"),
                      labels = c("Present","Missing")) +
    #scale_x_discrete(limits = levels) +
    labs(x = "Variable",
         y = "Row Number",
         title = "Missing values in rows") + 
    coord_flip()
  
  return(p)
}
na_vals(df)

rm(na_vals)
```
Normally there is a timestamp variable. This dataset doesn't provide one. I think it will be more 'fun' to not assume that there is a time series elements. So we could assume that these are occasional process samples taken.

The reason I mention that is because most of the blanks are at the front and at the end. More often than not, I'll run a linear interpolation for all the blanks inbetween and simply remove the first (and last) mostly blank rows.

For now, let's focus on modeling and just go after the full rows. According to this visual, we shouldn't lose a significant number of rows. Another fun option is predicting the non-target variables. Maybe later.

```{r}
df <- df %>% filter(complete.cases(.))

df %>% dim()
```
Calling that good enough. In the future we can look for outliers, but I want to move to modeling.

# Modeling 
From the previous visual, I can assume the problem is to predict the yield using the remaining data. I haven't learned tidy modeling to my preference, so I plan to walk through the examples in Max Kuhn's Tidy Modeling With R: tmwr.org

## Split data 
```{r}
set.seed(1234)
require(tidymodels)

chemproc_split <- initial_split(df, prop = 0.7)

chemproc_split
```
```{r}
chem_train <- training(chemproc_split)
chem_test <- testing(chemproc_split)
```
## Build the recipe 
I'll start by using all the variables to predict, this is almost never a good idea.
```{r}
simple_chem <- recipe(Yield ~ ., data = chem_train)

simple_chem
```
## Create models 
Start with the basics
```{r}
lm_model <- linear_reg() %>% set_engine("lm")

lm_model
```
```{r}
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(simple_chem)

lm_fit <- fit(lm_wflow, chem_train)
```
Can you imagine programming this in PI? This is where too many variables gets silly
```{r}
lm_fit
```
## Performance 
Not sure I like this process, wasn't a fan of bind_cols, understood it after trying to avoid with mutate (don't--that will save 15 minutes)
```{r}
chem_test_res <- predict(lm_fit, new_data = chem_test %>% select(-Yield)) %>% 
  bind_cols(., chem_test %>% select(Yield))
```

I've seen worse models to start with.
```{r}
chem_test_res %>% 
  ggplot(aes(x=Yield,y=.pred)) +
  geom_point() +
  geom_abline(lty = 2)
```
```{r}
chem_metrics <- metric_set(rmse, rsq, mae)

chem_metrics(chem_test_res, truth = Yield, estimate = .pred)
```

That gives us a starting place! Looking forward to any feedback!
